Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-08-22 BD_radvel/mn060888mj_rev/kurosawa.tex
Version ok-ed by Stu. Waiting for Tim's OK sign.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@791 25464f21-6099-402c-b30a-640f1d40d38b

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. 
  \textcolor{red}{The expected distribution (dashed) for RV constant
  objects is also shown for a comparison.} The distribution is
  normalized with the total number of objects that have $p<10^{-3}$.
  The match between the expected distribution and the
  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
  indicating that our uncertainty estimates 
  in RV values are also reasonable.  }

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
Finally, we note that the binary fraction found in this paper may be
over-estimated because of the nature of our survey (magnitude-limited
and incomplete), and because of a possible bias towards brighter
objects.
}

@@

% LocalWords:  BDs VLM OB Ophiuchi al Ryuichi Harries QL RV UScoOB BD echelle
% LocalWords:  VLT UVES RVs Cha bouy burgasser gizis kraus basri maxted PPl EEV
% LocalWords:  pinfield substellar duquennoy VLMs guenther joergens padoan CCDs
% LocalWords:  reipurth whitworth dezeeuw ardila luhman muzerolle Kueyen Parnal
% LocalWords:  LL ESO interorder autoguiding FWHM jones Oph wilking mohanty Sp
% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp AJ
% LocalWords:  obs ApJ PASP MNRAS Chamaeleon semimajor siegler Praesepe stassun
% LocalWords:  mccaughrean segransan tinney palla kenyon Jeffries Naylor Bromm
% LocalWords:  natexlab Reiners Bonnell Moraux Brandner Baraffe ndez McElwain
% LocalWords:  astro ph de Zeeuw de Zeeuw de Bruijne Hoogerwerf Lub Blaauw
% LocalWords:  Battrick

>>>>

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. 
  \textcolor{red}{The expected distribution (dashed) for RV constant
  objects is also shown for a comparison. The distribution is
  normalized with the total number of objects that have $p<10^{-3}$}.
  The match between the expected distribution and the
  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
  indicating that our uncertainty estimates 
  in RV values are also reasonable.  }

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
It is possible that out binary fraction is an overestimate since we
are biased to brighter objects. However the lack of a double-lined
system suggests that a primary-to-secondary luminosity ratio of $\gg 1$
for the RV variables found in this paper. 
}

@@

% LocalWords:  BDs VLM OB Ophiuchi al Ryuichi Harries QL RV UScoOB BD echelle
% LocalWords:  VLT UVES RVs Cha bouy burgasser gizis kraus basri maxted PPl EEV
% LocalWords:  pinfield substellar duquennoy VLMs guenther joergens padoan CCDs
% LocalWords:  reipurth whitworth dezeeuw ardila luhman muzerolle Kueyen Parnal
% LocalWords:  LL ESO interorder autoguiding FWHM jones Oph wilking mohanty Sp
% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp AJ
% LocalWords:  obs ApJ PASP MNRAS Chamaeleon semimajor siegler Praesepe stassun
% LocalWords:  mccaughrean segransan tinney palla kenyon Jeffries Naylor Bromm
% LocalWords:  natexlab Reiners Bonnell Moraux Brandner Baraffe ndez McElwain
% LocalWords:  astro ph de Zeeuw de Zeeuw de Bruijne Hoogerwerf Lub Blaauw VLTI
% LocalWords:  Battrick horne benedict Acknowledgements
